---
title: "Function Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Function Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Introducing the posterior Trace Package 
-A few words about your motivations in writing this R package/ What is it meant to do, what type of data does it wrok with 

## Installation Instructions 

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(devtools)
devtools::install_github("BennyShoe/Project_three")
library(SchusterRPackage)
```

## Where to get the data 
```{r}
library(readr)
library(googlesheets4)
gs4_deauth()
download.file("https://github.com/BennyShoe/Project_three/raw/refs/heads/main/data/R_Project1_Our_Data.csv","/cloud/project/data/Fish_Data.csv")

```


## Function one filters the data to remove NAs and juveniles from the dataset
```{r eval=FALSE}

Fish_Data <- read.csv("../data/Fish_Data.csv")

SchusterRPackage::Filter_Function(Fish_Data)
```
## Function two creates a violin plot 
```{r}

Fish_Data <- read.csv("../data/Fish_Data.csv")

library(ggplot2)
SchusterRPackage::Violin_Plot_Function(Fish_Data, SL, LL, Sex, "Sex", "SL", "LL")

```

## Function three allows you to check to see if fish in selected column are too small
```{r}
Fish_Data <- read.csv("../data/Fish_Data.csv")
library(dplyr)
SchusterRPackage::my_function(Fish_Data, SL, 25)

```

## Function four Calculates three ratios of a selected columns and adds a new columns the dataset with those values
```{r}

Fish_Data <- read.csv("../data/Fish_Data.csv")
SchusterRPackage::Ratio_Function(Fish_Data, SL, LL, TV)

```

## Fucntion five creates a linear model graph
```{r}
Fish_Data <- read.csv("../data/Fish_Data.csv")
library(ggplot2)
SchusterRPackage::LM_Graph_Function(Fish_Data, "SL", "LL")

```

## Function six creates  various linear model tests to see if your data is normally distributed
```{r}
Fish_Data <- read.csv("../data/Fish_Data.csv")
library(ggplot2)
SchusterRPackage::LM_Function(Fish_Data, "SL", "LL")

```
