---
title: "Function Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Function Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Introducing the posterior Trace Package 
-A few words about your motivations in writing this R package/ What is it meant to do, what type of data does it wrok with 

## Installation Instructions 


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
devtools::install_github("BennyShoe/Project_three")
library(SchusterRPackage)
```

## Where to get the data 
-Could use google sheets 
-Can stash data in an R package 


##Function one filters the data to remove NAs and juveniles from the dataset
```{r}
SchusterRPackage::Filter_Function()
```
##Function two creates a violin plot 
```{r}

SchusterRPackage::Graph_Function()

```

##Function three allows you to check to see if fish in selected column are too small
```{r}

SchusterRPackage::my_function()

```

##Function four Calculates three ratios of a selected columns and adds a new columns the dataset with those values
```{r}

SchusterRPackage::Ratio_Function()

```

##Fucntion five creates a linear model graph
```{r}

SchusterRPackage::LM_Graph_Function()

```

##Function six crates various linear model tests to see if your data is normally disturbed
```{r}

SchusterRPackage::LM_Function()

```
